detrendr examples

### 2017-06-20 Notes/timing_and_convergence_examples.Rmd
updates to timing comparisons

simulate <- function(n, k){
  x <- seq(1/n, 1, length.out=n)
  f <- 2*(x + 2)^2 + 3*cos(3*pi*x)
  tau <- 5e4
  g1 <- 40*exp(-tau*(x-0.3)^2)
  g2 <- 30*exp(-tau/2*(x-0.58)^2)
  g4 <- 45*exp(-tau/7*(x-0.6)^2)
  g3 <- 37*exp(-tau*(x-0.63)^2)
  y <- f + g1 + g2 + g3 + g4 + rnorm(n)
  D <- get_Dk(n, k)
  M <- diag(n) + crossprod(D)
  cholM <- chol(M)
  return(list(y=y, f=f, x=x, D=D, M=M, cholM=cholM))
}
```

## Current timing experiments
```{r timing, include=TRUE, echo=TRUE, cache=TRUE}
nSeq <- seq(500, 4500, 500)
timing <- data.frame(n=nSeq, R = NA, C=NA)
tau <- 0.01
lambda0 <- .000001
step <- 1
k <- 4

for (i in 1:length(nSeq)){
  simData <- simulate(nSeq[i], k)
  lambda <- lambda0*nSeq[i]^k/factorial(k)
  y <- simData$y
  theta <- simData$y
  D <- simData$D
  eta <- matrix(D%*%theta)
  M <- simData$M
  cholM <- simData$cholM
  timing$R[i] <- system.time( 
      multi_step_R <- spingarn_multi_step_R(theta, eta, y, D, M, lambda, tau, step, 100))[3]
  timing$C[i] <- system.time(
    multi_step <- spingarn_multi_step(theta, eta, y, D, cholM,
                                     lambda, tau, step, 100, k))[3]
}

plot(C~n, timing, type="l", col="blue", ylab="Elapsed Time (s) per 100 iterations", main = "R code is in black, C in blue", ylim = c(0, 1))
lines(R~n, timing, type="l")
```

>>>>

simulate <- function(n, k){
  x <- seq(1/n, 1, length.out=n)
  f <- 2*(x + 2)^2 + 3*cos(3*pi*x)
  tau <- 5e4
  g1 <- 40*exp(-tau*(x-0.3)^2)
  g2 <- 30*exp(-tau/2*(x-0.58)^2)
  g4 <- 45*exp(-tau/7*(x-0.6)^2)
  g3 <- 37*exp(-tau*(x-0.63)^2)
  y <- f + g1 + g2 + g3 + g4 + rnorm(n)
  D <- get_Dk(n, k)
  M <- diag(n) + crossprod(D)
  cholM <- Matrix::chol(M)
  return(list(y=y, f=f, x=x, D=D, M=M, cholM=cholM))
}

compareTimeR <- function(n){
  simData <- simulate(n, k)
  lambda <- lambda0*n^k/factorial(k)
  y <- simData$y
  theta <- simData$y
  D <- simData$D
  eta <- matrix(D%*%theta)
  M <- simData$M
  cholM <- simData$cholM
  spingarn_multi_step_R(theta, eta, y, D, M, lambda, tau, step, 500)
}

compareTimeC <- function(n){
  simData <- simulate(n, k)
  lambda <- lambda0*n^k/factorial(k)
  y <- simData$y
  theta <- simData$y
  D <- simData$D
  eta <- matrix(D%*%theta)
  M <- simData$M
  cholM <- simData$cholM
  spingarn_multi_step(theta, eta, y, D, M, lambda, tau, step, 500)
}
```

## Current timing experiments
```{r timing, include=TRUE, echo=TRUE, cache=TRUE}
nSeq <- seq(200, 3000, 200)
timing <- data.frame(n=nSeq, R_mean = NA, R_lq = NA, R_uq = NA,
                             C_mean=NA, C_lq=NA, C_uq = NA)
tau <- 0.01
lambda0 <- 1e-8
step <- 1
k <- 3

for (i in 1:length(nSeq)){

  set.seed(38912498)
  Rbench <- microbenchmark(compareTimeR(nSeq[i]), times=100)
  set.seed(38912498)
  Cbench <- microbenchmark(compareTimeC(nSeq[i]), times=100)

  timing$R_mean[i] <- median(Rbench$time*1e-9)
  timing$R_lq[i] <- quantile(Rbench$time*1e-9, .25)
  timing$R_uq[i] <- quantile(Rbench$time*1e-9, .75)
  timing$C_mean[i] <- median(Cbench$time*1e-9)
  timing$C_lq[i] <- quantile(Cbench$time*1e-9, .25)
  timing$C_uq[i] <- quantile(Cbench$time*1e-9, .75)
  print(i)
}

library(microbenchmark)

plot(C_mean~n, timing, type="l", col="blue", ylab="Elapsed Time (s)' per 500 iterations", main = "R code is in black, C in blue")
lines(C_lq~n, timing, col="blue")
lines(C_uq~n, timing, col="blue")
lines(R_mean~n, timing, type="l")
```
